\begin{frame}
    Instructions: \pause
    \begin{itemize}
    \item Submit a \textbf{zip} file containing your report in \textbf{pdf} format and your code. \pause
    \item \textbf{Deadline}: Monday night following at 11:59 PM. \pause
    \item Report: \pause
    \begin{itemize}
    \item Answers to the TD questions. Figures and numerical results are necessary but not sufficient: provide your analysis/comments as well. \pause
    \item Example: if your results surprise you, explain why and explain what the expected result was. \pause
    \item Pay attention to the presentation: axis labels, legend, etc. \pause
    \end{itemize}
    \item Code: \pause
    \begin{itemize}
        \item Implementation questions + code used to produce the results and figures in the report. \pause
        \item Programming language of your choice. \pause
        \item We recommend Python: I won't be able to assist you in the same way if you use a different language.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
Session organization: \pause
\vspace{1cm}
\begin{enumerate}
\item Answers to your questions from the previous session. \pause
\item Comments on the series I've just corrected. \pause
\item Presentation of today's series. \pause
\item Today's series.
\end{enumerate}
\end{frame}

\begin{frame}
Questions during the week: \pause
\vspace{1cm}
\begin{itemize}
\item On \textbf{Discord} rather than via email. \pause
\item Any question is good, even if (especially if?) you feel it's stupid. \pause
\item The answer is probably of interest to other students. \pause
\item Don't hesitate to contribute to the answer if you think you can help.
\end{itemize}
\end{frame}

\begin{frame}
Important reminder: you must have completed 8 exercise series out of 13 to be eligible for the final exam.
\end{frame}

\begin{frame}
Fill out the "about you" questionnaire on Moodle (2 minutes, to know your background).
\end{frame}




