\section{Algorithm based on price evolution}
Finally, implement an execution algorithm that takes into account the price evolution. For instance, you can split the order into 12 equal slices and trade a slice at each downward directional change $\delta$. 
\begin{itemize}
    \item Picking again the same initial times, compute the execution prices you got with this method and compare them with the ones previously obtained. 
    \item How should you choose $\delta$ to execute the full order over 3 hours?
\end{itemize}

\section{Impact of Market Volatility}
In this task, you will analyze how market volatility affects the execution prices obtained using different execution strategies (TWAP, VWAP, and the price-evolution-based method). 
\begin{enumerate}
    \item \textbf{Compute Market Volatility:} 
    \begin{itemize}
        \item Define volatility as the standard deviation of mid-price returns over a rolling window of 30 minutes.
        \item Compute this measure for the selected 20 time intervals.
    \end{itemize}
    \item \textbf{Analyze Execution Performance Under Different Volatility Conditions:}
    \begin{itemize}
        \item Divide the 20 intervals into two groups:
        \begin{itemize}
            \item \textbf{Low-volatility periods:} Where the rolling standard deviation is in the bottom 50\% of the dataset.
            \item \textbf{High-volatility periods:} Where the rolling standard deviation is in the top 50\%.
        \end{itemize}
        \item Compute and compare the execution prices obtained using TWAP, VWAP, and price-evolution strategies across both groups. Which strategy performs best in volatile markets?
        \item Is there a strategy that minimizes execution price deviation across all market conditions?
    \end{itemize}
\end{enumerate}